---
title: "Data Quality Report – multimodal alignment"
format:
  html:
    toc: true
    toc-depth: 2
    number-sections: true
    code-fold: true
    code-tools: true
    code-summary: "Mostrar código"
    code-overflow: wrap
    theme: flatly
    highlight-style: github
    self-contained: true
---

# Corroboroation today

```{r setup}
library(dplyr)
library(ggplot2)
library(scales)
# cualquier otro que uses
load("multi_df.rda")
```

```{r}

library(tidyverse)


print(dim(multi_df))


# Verificar proporción de valores válidos
multi_df %>%
  filter(!is.na(words) & words != "") %>%
  summarise(
    pitch_valid     = mean(!is.na(pitch)),
    intensity_valid = mean(!is.na(intensity)),
    keypoints_valid = mean(!is.na(nx) & !is.na(ny))
  )
# Resultado esperado:
# pitch_valid     = 1
# intensity_valid = 1
# keypoints_valid ≈ 0.914

# Detectar outliers extremos en coordenadas (OpenPose fallos)
multi_df %>%
  filter(abs(nx) > 5 | abs(ny) > 5) %>%
  count(type_points, sort = TRUE)
# Resultado típico:
# type_points            n
# pose_keypoints     776245
# hand_right_keypoints 481638
# etc.

# Verificar proporción de palabras ausentes por ID
multi_df %>%
  group_by(id) %>%
  summarise(
    total_frames = n(),
    missing_pitch = mean(is.na(pitch)),
    missing_intensity = mean(is.na(intensity)),
    missing_words = mean(is.na(words) | words == ""),
    missing_nx = mean(is.na(nx)),
    missing_ny = mean(is.na(ny))
  ) %>%
  arrange(desc(missing_words)) %>%
  print(n = 10)

```

| Feature            | Status           | Notes                                                   |
|----------------|----------------|-----------------------------------------|
| Frame alignment    | ✅ OK            | Synchronization confirmed with animated overlays        |
| Keypoints coverage | ⚠️ \~91.4% valid | Missing in \~8.6% of points (e.g. occlusion, low light) |
| Pitch              | ✅ 100% valid    | No missing values in any frame                          |
| Intensity          | ✅ 100% valid    | No missing values in any frame                          |
| Word alignment     | ✅ Expected      | Gaps reflect silent frames or between-word regions      |
| Outlier filtering  | ❌ Not yet       | Extreme keypoints present (e.g. `abs(nx/ny) > 5`)       |



# Plots

## Visual Inspection – Gesture and Prosody

The following plot illustrates the synchronisation of vertical wrist movement (`ny`) with prosodic cues (intensity and pitch), using frame-based alignment.




```{r}
# ───────────────────────── parameters ──────────────────────────
target_id     <- "2016-01-12_0100_US_KNBC_Channel_4_News_1171.022_1175.056_today"
person_target <- 1
n_frames      <- 120            # tweak length if desired
out_width_cm  <- 14
out_height_cm <- 18

# ────────────────────── data preparation ───────────────────────
library(dplyr); library(stringr); library(scales)

df_id <- multi_df |>                       # multi_df already in memory
  filter(id == target_id, people_id == person_target) |>
  mutate(type = str_remove(type_points, "_keypoints$"),
         type = recode(type,
                       hand       = "hand_left",
                       hand_left  = "hand_left",
                       hand_right = "hand_right"),
         frame = as.integer(frame)) |>
  arrange(frame)

frames_sel <- sort(unique(df_id$frame))[seq_len(n_frames)]

df_sel <- df_id |>                          # keep only the subset
  filter(frame %in% frames_sel) |>
  mutate(frame_rel = frame - min(frame) + 1)  # zero-based time axis

# wrist = right hand, point 0 (OpenPose convention)
df_wrist <- df_sel |>
  filter(type == "hand_right", points == 0) |>
  select(frame_rel, ny, words) |>
  mutate(words = ifelse(is.na(words) | words == "", "###", words)) |>
  # order words by first appearance
  mutate(words = factor(words, levels = unique(words)))

df_int   <- df_sel |>
  group_by(frame_rel) |>
  summarise(intensity = mean(intensity, na.rm = TRUE), .groups = "drop") |>
  mutate(int_norm = rescale(intensity, to = c(0, 1)))

df_pitch <- df_sel |>
  group_by(frame_rel) |>
  summarise(pitch = mean(pitch, na.rm = TRUE), .groups = "drop") |>
  mutate(pitch_norm = rescale(pitch, to = c(0, 1)))

# ────────────────────────── plotting ───────────────────────────
library(ggplot2); library(patchwork)

p_wrist <- ggplot(df_wrist, aes(frame_rel, ny, colour = words)) +
  geom_line(colour = "grey80") +
  geom_point(size = 2) +
  scale_colour_viridis_d(end = .85, option = "turbo") +
  coord_cartesian(ylim = range(df_wrist$ny, na.rm = TRUE)) +
  labs(title   = "Right-wrist vertical displacement",
       y       = "ny (normalised)",
       x       = "Frame",
       colour  = "Word") +
  theme_classic(base_size = 9) +
  theme(legend.position = "bottom",
        legend.title    = element_text(size = 8),
        legend.key.size = unit(0.3, "cm"))

p_int <- ggplot(df_int, aes(frame_rel, int_norm)) +
  geom_line(colour = "orange", linewidth = 0.8) +
  geom_point(colour = "orange", size = 1.5) +
  labs(title = "Intensity (normalised)",
       y     = "Intensity",
       x     = "Frame") +
  theme_classic(base_size = 9)

p_pitch <- ggplot(df_pitch, aes(frame_rel, pitch_norm)) +
  geom_line(colour = "steelblue", linewidth = 0.8) +
  geom_point(colour = "steelblue", size = 1.5) +
  labs(title = "Fundamental frequency (normalised)",
       y     = "F0",
       x     = "Frame") +
  theme_classic(base_size = 9)

fig_static <- p_wrist / p_int / p_pitch +
  plot_annotation(
    title    = "Synchrony of Gesture and Prosody",
    subtitle = target_id,
    theme    = theme(plot.title = element_text(size = 11, face = "bold"),
                     plot.subtitle = element_text(size = 8))
  )

ggsave(sprintf("gesture_prosody_%s.png", target_id),
       fig_static, width = out_width_cm, height = out_height_cm,
       units = "cm", dpi = 300)



```



```{r}
fig_static <- p_wrist / p_int / p_pitch +
  plot_annotation(
    title    = "Synchrony of Gesture and Prosody",
    subtitle = target_id,
    caption  = "Figure: Right wrist vertical movement across frames aligned with pitch and intensity (normalized). Color encodes spoken words in temporal order.",
    theme    = theme(
      plot.title    = element_text(size = 11, face = "bold"),
      plot.subtitle = element_text(size = 8, margin = margin(b = 6)),
      plot.caption  = element_text(size = 8, hjust = 0)
    )
  )
```



```{r}
fig_static
```

